Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2025-05-26 src/naomi-simple_ks/ks.Rmd
Improve KS summary figure

ks_summary_latent <- filter(ks_summary, type == "Latent")

@@

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq - TMB, col = parname, size = size)) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed") +
  labs(x = "KS(GEB, NUTS)", y = "KS(GPCA-AGHQ, NUTS) - KS(GEB, NUTS)", col = "Parameter", size = "Length") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top")) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.65)))

ggsave("ks-summary.png", h = 5, w = 6.25, bg = "white")
```

>>>>

fct_case_when <- function(...) {
  args <- as.list(match.call())
  levels <- sapply(args[-1], function(f) f[[3]])  # extract RHS of formula
  levels <- levels[!is.na(levels)]
  factor(dplyr::case_when(...), levels=levels)
}

# Include group information
ks_summary_latent <- filter(ks_summary, type == "Latent") %>%
  mutate(
    component = fct_case_when(
      parname %in% c("beta_rho", "u_rho_a", "u_rho_as", "u_rho_x", "u_rho_xs", "us_rho_x", "us_rho_xs") ~ "HIV prevalence",
      parname %in% c("beta_lambda", "ui_lambda_x") ~ "HIV incidence",
      parname %in% c("beta_alpha", "u_alpha_a", "u_alpha_as", "u_alpha_x", "u_alpha_xs", "us_alpha_x", "us_alpha_xs", "u_alpha_xa", "ui_anc_alpha_x", "ui_anc_rho_x", "log_or_gamma") ~ "ART coverage",
      TRUE ~ "Other"
    ),
    label = fct_case_when(
      parname %in% c("beta_alpha", "beta_rho", "beta_lambda") ~ "Intercept",
      parname %in% c("u_alpha_a", "u_rho_a") ~ "Age effect",
      parname %in% c("u_alpha_x", "u_alpha_xs", "u_rho_x", "us_rho_x", "us_alpha_x", "ui_lambda_x", "ui_anc_alpha_x", "ui_anc_rho_x") ~ "Space effect",
      parname %in% c("u_alpha_as", "u_rho_as", "u_alpha_xa") ~ "Age-sex effect",
      parname %in% c("us_rho_xs", "us_alpha_xs", "u_rho_xs") ~ "Space-sex effect",
      parname %in% c("log_or_gamma") ~ "Log odds ratio",
      TRUE ~ "Other"
    )
  )

@@

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq - TMB, col = label, size = size)) +
  facet_wrap(~ component, ncol = 1) +
  geom_point(shape = 1) +
  scale_color_manual(values = multi.utils::cbpalette()) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed", col = "grey") +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32), range = c(2, 4)) +
  scale_y_continuous(limits = c(-0.08, 0.08)) +
  labs(x = "Average of KS(GEB)", y = "Average of KS(GPCA-AGHQ) - KS(GEB)", col = "Parameter type", size = "Parameter length") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "horizontal"), col = guide_legend(title.position = "top", nrow = 6, byrow = TRUE)) +
  theme(
    legend.position = "right",
    legend.title = element_text(size = rel(0.9)),
    legend.text = element_text(size = rel(0.9)),
    panel.spacing.y = unit(1.2, "lines")
  )

ggsave("ks-summary.png", h = 5.25, w = 6.25, bg = "white")
```
